quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-06-04 paper-quollr.Rmd
Adding suggestion for appropriate model for prism
Added intro for prism data

@@

@@

triangular_3d_data <- triangular_3d_data |>
  mutate(ID = row_number())

tSNE_fit <- triangular_3d_data |>
  select(-ID) |>
  Rtsne(perplexity = sqrt(NROW(triangular_3d_data)))

@@

>>>>

<!--add intro to prism data-->

To illustrate the method, we use $5\text{-}D$ simulated data, which we call the "triangular_3d_data". This dataset is generated using the `tri_3d` function from the `cardinalR` package. The dataset generation starts with the initialization of a starting point $p_0 = (x_0, y_0, z_0)$ randomly selected within the $3\text{-}D$ space using a uniform distribution. Four fixed corner points of a tetrahedron are defined as $c_1 = (0, 0, 0)$, $c_2 = (1, 0, 0)$, $c_3 = (0.5, 1, 0)$, and $c_4 = (0.5, 0.5, 1)$. For each point $p_i$ where $i = 1, 2, \ldots, n$, one of the corner points $c_j$ (where $j \in \{1, 2, 3, 4\}$) is selected randomly, and the new point $p_i$ is computed as the midpoint between the current point $p_{i-1}$ and the selected corner point $c_j$: $p_i = \frac{p_{i-1} + c_j}{2}$. This iterative process ensures that each new point moves closer to one of the corners, creating a fractal-like triangular distribution of points. The coordinates of each generated point $p_i$ form the variables $X_1, X_2, X_3$. The remaining variables $X_4, X_5$ are all uniform error, with small variance. We would consider $T=(X_1, X_2, X_3)$ to be the true model.

<!-- hoe the data are generated and from which package I got the data-->

@@

```{r}
triangular_3d_data <- triangular_3d_data |>
  mutate(ID = row_number())
```

<!--added, I selected tSNE with perplexity = 35 to explore and -->

@@

tSNE_fit <- triangular_3d_data |>
  select(-ID) |>
  Rtsne(perplexity = round(sqrt(NROW(triangular_3d_data))))

@@

## Selecting parameter values for the model
